Decentralized Active Damping of Rotating Positioning Platforms

### 2020-06-25 paper/paper.tex
Add equations

% Created 2020-06-25 jeu. 10:07
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Decentralized Active Damping of Rotating Positioning Platforms}
\hypersetup{
 pdfauthor={},
 pdftitle={Decentralized Active Damping of Rotating Positioning Platforms},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:org5780a8f}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).
This paper has been published
The Matlab code that was use to obtain the results are available in \cite{dehaeze20_activ_dampin_rotat_posit_platf}.

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:orga8db619}
\subsection{Studied Rotating Positioning Platform}
\label{sec:org70ddefe}
Consider the rotating X-Y stage of Figure \ref{fig:system}.

@@

\subsection{Equations of Motion}
\label{sec:org647b64d}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \([q_1\ q_2] = [d_u\ d_v]\) (describing the position of the mass in the rotating frame).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:org55c9228}

@@

\subsection{Change of Variables / Parameters for the study}
\label{sec:orgb7d090c}

@@

\subsection{System Dynamics and Campbell Diagram}
\label{sec:org24f5f5f}
The bode plot of \(\bm{G}_d\) is shown in Figure \ref{fig:plant_compare_rotating_speed}.

@@

@@

\section{Decentralized Integral Force Feedback}
\label{sec:orgd957fd6}
\subsection{Control Schematic}
\label{sec:orgc01d8cf}

@@

\subsection{Equations}
\label{sec:orge5896ec}
The forces measured by the force sensors are equal to:
\begin{equation}
\label{eq:measured_force}
  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

Reinjecting \eqref{eq:tf_d} into \eqref{eq:measured_force} yields:
\begin{equation}
\label{eq:tf_f}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\bm{G}_f =
\frac{1}{G_{fp}}
\begin{bmatrix}
  G_{fz} & -G_{fc} \\
  G_{fc} &  G_{fz}
\end{bmatrix}
\end{equation}

\begin{align}
  G_{fp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)
\end{align}

\begin{equation}
\bm{G}_f =
\frac{1}{\left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2}
\begin{bmatrix}
  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 & -G_{fc} \\
  G_{fc} &  \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2
\end{bmatrix}
\end{equation}

\subsection{Plant Dynamics}
\label{sec:org0a22a10}

@@

\subsection{Problems with Integral Force Feedback}
\label{sec:orgd432439}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org2e1883a}
\subsection{Modification of the Control Low}
\label{sec:org218110f}
\begin{equation}
  \bm{K}_{F}(s) = \frac{1}{s} \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = \frac{1}{s + \omega_i}
\end{equation}

\subsection{Feedback Analysis}
\label{sec:org03090fc}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF}
\end{figure}

@@

\subsection{Optimal Cut-Off Frequency}
\label{sec:org6ba4e55}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org90ec20f}
\subsection{Stiffness in Parallel with the Force Sensor}
\label{sec:org60d6640}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_parallel_springs.pdf}
\caption{\label{fig:system_parallel_springs}System with added springs \(k_p\) in parallel with the actuators}
\end{figure}

@@

\begin{equation}
\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
\frac{1}{G_{kp}}
\begin{bmatrix}
   G_{kz} & -G_{kc} \\
   G_{kc} &  G_{kz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
With:
\begin{align}
  G_{kp} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
  G_{kz} &= \left( \frac{s^2}{{\omega_0^\prime}^2} + \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) \left( \frac{s^2}{{\omega_0^\prime}^2} + 2\xi^\prime \frac{s}{{\omega_0^\prime}^2} + 1 - \frac{\Omega^2}{{\omega_0^\prime}^2} \right) + \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)^2 \\
  G_{kc} &= \left( 2 \xi^\prime \frac{s}{\omega_0^\prime} + \frac{k}{k + k_p} \right) \left( 2 \frac{\Omega}{\omega_0^\prime}\frac{s}{\omega_0^\prime} \right)
\end{align}

where:
\begin{itemize}
\item \(\omega_0^\prime = \frac{k + k_p}{m}\)
\item \(\xi^\prime = \frac{c}{2 \sqrt{(k + k_p) m}}\)
\end{itemize}

\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
\label{sec:org3ec34fe}

\begin{equation}
  \frac{k_p}{k + k_p} - \frac{\Omega^2}{{\omega_0^\prime}^2} > 0
\end{equation}
Which is equivalent to
\begin{equation}
  k_p > m \Omega^2
\end{equation}

@@

\subsection{Optimal Parallel Stiffness}
\label{sec:org9c47159}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
\caption{\label{fig:root_locus_iff_kps}Root Locus for IFF for several parallel spring stiffnesses \(k_p\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_opt_gain_iff_kp.pdf}
\caption{\label{fig:root_locus_opt_gain_iff_kp}Root Locus for IFF with \(k_p = 5 m \Omega^2\). The poles of the system using the gain that yields the maximum damping ratio are shown by black crosses}
\end{figure}

\section{Direct Velocity Feedback}
\label{sec:org5cb3076}
\subsection{Control Schematic}
\label{sec:orgaaa522f}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_dvf.pdf}
\caption{\label{fig:system_dvf}System with relative velocity sensors and with decentralized controllers \(K_V\)}
\end{figure}

\subsection{Equations}
\label{sec:orge0a4555}

@@

\begin{equation}
\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
\frac{s}{k} \frac{1}{G_{vp}}
\begin{bmatrix}
   G_{vz} & G_{vc} \\
  -G_{vc} & G_{vz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
With:
\begin{align}
  G_{vp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{vz} &= \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \\
  G_{vc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
\end{align}

\subsection{Relative Direct Velocity Feedback}
\label{sec:org5401110}

@@

\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
\label{sec:org4cbf163}
\subsection{Physical Comparison}
\label{sec:org5eba275}

\subsection{Attainable Damping}
\label{sec:org44635e0}

@@

\subsection{Transmissibility and Compliance}
\label{sec:org58e9594}

@@

\section{Conclusion}
\label{sec:org292b448}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:orgff7af07}

>>>>

% Created 2020-06-25 jeu. 17:24
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Decentralized Active Damping of Rotating Positioning Platforms}
\hypersetup{
 pdfauthor={},
 pdftitle={Decentralized Active Damping of Rotating Positioning Platforms},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:org7ff5c70}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).
Due to gyroscopic effects, the guaranteed robustness properties of Integral Force Feedback do not hold.
Either the control architecture can be slightly modfied or mechanical changes in the system can be performed.
This paper has been published
The Matlab code that was use to obtain the results are available in \cite{dehaeze20_activ_dampin_rotat_posit_platf}.

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:org029ca48}
\subsection{Studied Rotating Positioning Platform}
\label{sec:org7eec6c5}
Consider the rotating X-Y stage of Figure \ref{fig:system}.

@@

\subsection{Equations of Motion}
\label{sec:orgca181a2}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \([q_1\ q_2] = [d_u\ d_v]\) (describing the position of the mass in the rotating frame).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:orge7e184a}

@@

\subsection{Change of Variables / Parameters for the study}
\label{sec:org3cdb1ab}

@@

\begin{itemize}
\item \(k = \SI{1}{N/m}\), \(m = \SI{1}{kg}\), \(c = \SI{0.05}{\newton\per\meter\second}\)
\item \(\omega_0 = \SI{1}{\radian\per\second}\), \(\xi = 0.025\)
\end{itemize}

\subsection{System Dynamics and Campbell Diagram}
\label{sec:org42dee20}
The bode plot of \(\bm{G}_d\) is shown in Figure \ref{fig:plant_compare_rotating_speed}.

@@

The poles are the roots of \(G_{dp}\).
Two pairs of complex conjugate poles (supposing small damping \(\xi \approx 0\)):
\begin{subequations}
  \begin{align}
    p_1 &= \pm j (\omega_0 - \Omega) \\
    p_2 &= \pm j (\omega_0 + \Omega)
  \end{align}
\end{subequations}

@@

\section{Decentralized Integral Force Feedback}
\label{sec:orgda38ad7}
\subsection{System Schematic and Control Architecture}
\label{sec:orgf08eb9d}

@@

\subsection{Plant Dynamics}
\label{sec:orgf2f22c2}
The forces measured by the force sensors are equal to:
\begin{equation}
\label{eq:measured_force}
  \begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
  \begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
  \begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

Re-injecting \eqref{eq:tf_d} into \eqref{eq:measured_force} yields:
\begin{equation}
\label{eq:tf_f}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} = \bm{G}_{f} \begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
Where \(\bm{G}_f\) is a \(2 \times 2\) transfer function matrix.

\begin{equation}
\bm{G}_f =
\frac{1}{G_{fp}}
\begin{bmatrix}
  G_{fz} & -G_{fc} \\
  G_{fc} &  G_{fz}
\end{bmatrix}
\end{equation}
with:
\begin{align}
  G_{fp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)
\end{align}

The zeros of the diagonal terms are the roots of \(G_{fz}\) (supposing small damping):
\begin{subequations}
  \begin{align}
    z_1 &= \pm j \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} + \frac{\Omega^2}{{\omega_0}^2} + \frac{1}{2} } \\
    z_2 &= \pm   \omega_0 \sqrt{\frac{1}{2} \sqrt{8 \frac{\Omega^2}{{\omega_0}^2} + 1} - \frac{\Omega^2}{{\omega_0}^2} - \frac{1}{2} }
  \end{align}
\end{subequations}

The frequency of the two complex conjugate zeros \(z_1\) is between the frequency of the two pairs of complex conjugate poles \(p_1\) and \(p_2\).
This is the expected behavior of a collocated pair of actuator and sensor.

However, the two real zeros \(z_2\) induces an increase of +2 of the slope without change of phase (Figure \ref{fig:plant_iff_compare_rotating_speed}).
This represents non-minimum phase behavior.

The low frequency gain, for \(\Omega < \omega_0\), is no longer zero:
\begin{equation}
\label{low_freq_gain_iff_plan}
  \bm{G}_{f0} = \lim_{\omega \to 0} \left| \bm{G}_f (j\omega) \right| = \begin{bmatrix}
  \frac{- \Omega^2}{{\omega_0}^2 - \Omega^2} & 0 \\
  0  & \frac{- \Omega^2}{{\omega_0}^2 - \Omega^2}
\end{bmatrix}
\end{equation}

It increase with the rotational speed \(\Omega\).

@@

\subsection{Decentralized Integral Force Feedback}
\label{sec:orge1a14b4}

\begin{equation}
  \bm{K}_F(s) = g \cdot \frac{1}{s}
\end{equation}

Also, as one zero has a positive real part, the \textbf{IFF control is no more unconditionally stable}.
This is due to the fact that the zeros of the plant are the poles of the closed loop system with an infinite gain.
Thus, for some finite IFF gain, one pole will have a positive real part and the system will be unstable.

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org7f551f8}
\subsection{Modification of the Control Low}
\label{sec:org4c39c6d}
\begin{equation}
  \bm{K}_{F}(s) = g \cdot \frac{1}{s} \cdot \underbrace{\frac{s/\omega_i}{1 + s/\omega_i}}_{\text{HPF}} = g \cdot \frac{1}{s + \omega_i}
\end{equation}

\subsection{Feedback Analysis}
\label{sec:org2673698}
\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF}
\end{figure}

\begin{equation}
  g_\text{max} = \omega_i \left( \frac{{\omega_0}^2}{\Omega^2} - 1 \right) \label{eq:iff_gmax}
\end{equation}

@@

\subsection{Optimal Cut-Off Frequency}
\label{sec:org7d8a789}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org9bc19d0}
\subsection{Stiffness in Parallel with the Force Sensor}
\label{sec:orgdfd59fa}
\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_parallel_springs.pdf}
\caption{\label{fig:system_parallel_springs}System with added springs in parallel with the actuators}
\end{figure}

\subsection{Plant Dynamics}
\label{sec:org70fc8fa}

We define an adimensional parameter \(\alpha\), \(0 \le \alpha < 1\), that describes the proportion of the stiffness in parallel with the actuator and force sensor:
\begin{subequations}
  \begin{align}
    k_p &= \alpha k \\
    k_a &= (1 - \alpha) k
  \end{align}
\end{subequations}

The overall stiffness \(k\) stays constant:
\begin{equation}
  k = k_a + k_p
\end{equation}

@@

\begin{equation}
\begin{bmatrix} f_u \\ f_v \end{bmatrix} =
\frac{1}{G_{kp}}
\begin{bmatrix}
   G_{kz} & -G_{kc} \\
   G_{kc} &  G_{kz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
With:
\begin{subequations}
  \begin{align}
    G_{kp} &= \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{\omega_0} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
    G_{kz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} + \alpha \right) \left( \frac{s^2}{{\omega_0}^2} + 2\xi \frac{s}{\omega_0} + 1 - \frac{\Omega^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)^2 \\
    G_{kc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 - \alpha \right) \left( 2 \frac{\Omega}{\omega_0}\frac{s}{\omega_0} \right)
  \end{align}
\end{subequations}

\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
\label{sec:orge20adc9}
\begin{equation}
  \begin{align}
    \alpha > \frac{\Omega^2}{{\omega_0}^2} \\
    \Leftrightarrow k_p > m \Omega^2
  \end{align}
\end{equation}

@@

\subsection{Optimal Parallel Stiffness}
\label{sec:orgb14b5c2}
\begin{figure}[htbp]
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
\caption{\label{fig:root_locus_iff_kps} Three values of \(k_p\)}
\end{subfigure}
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/root_locus_opt_gain_iff_kp.pdf}
\caption{\label{fig:root_locus_opt_gain_iff_kp} \(k_p = 5 m \Omega^2\), optimal damping is shown}
\end{subfigure}
\caption{\label{fig:root_locus_iff_kps_opt}Root Locus for IFF when parallel stiffness is used}
\centering
\end{figure}

\section{Direct Velocity Feedback}
\label{sec:org7628683}
\subsection{System Schematic and Control Architecture}
\label{sec:org6953bc7}
\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_dvf.pdf}
\caption{\label{fig:system_dvf}System with relative velocity sensors and with decentralized controllers \(K_V\)}
\end{figure}

\subsection{Equations}
\label{sec:orgfab42cd}

@@

\begin{equation}
\begin{bmatrix} v_u \\ v_v \end{bmatrix} =
\frac{1}{k} \frac{1}{G_{vp}}
\begin{bmatrix}
   G_{vz} & G_{vc} \\
  -G_{vc} & G_{vz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}
With:
\begin{subequations}
  \begin{align}
    G_{vp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
    G_{vz} &= s \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) \\
    G_{vc} &= 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0}
  \end{align}
\end{subequations}

\subsection{Relative Direct Velocity Feedback}
\label{sec:org5cf0d6b}

@@

\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
\label{sec:orga2b60a8}
\subsection{Physical Comparison}
\label{sec:orgb69316c}

\subsection{Attainable Damping}
\label{sec:org5c23e13}

@@

\subsection{Transmissibility and Compliance}
\label{sec:org723fb63}

@@

\section{Conclusion}
\label{sec:orgd52b568}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:orge4d73e9}
